\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\hypersetup{
  pdftitle={Euclidean Support Modes of the Regular Dodecahedron},
  pdfauthor={Scott Allen Cave},
  pdfsubject={Euclidean convex geometry and dodecahedral support modes}
}

\setcounter{tocdepth}{1}
\setcounter{secnumdepth}{2}
\raggedbottom

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{Euclidean Support Modes of the Regular Dodecahedron\\
\large Scale, Shape, and Symmetry from Six Opposite-Face Distances}
\author{Scott Allen Cave}
\date{July 11, 2026}

\begin{document}

\maketitle

\begin{abstract}
This paper develops a Euclidean scale-shape decomposition for a
six-parameter family based on the regular dodecahedron. Fix the twelve
regular dodecahedral face-normal directions and assign one positive support
number to each of the six opposite-face pairs. Their supporting slabs
intersect in an origin-centered, centrally symmetric convex polytope.

The resulting support register lies in \(\mathbb R^6\) and decomposes
orthogonally into a one-dimensional uniform subspace and a
five-dimensional zero-mean subspace. Common multiplication of all six
support numbers produces Euclidean homothety. While the defining planes
remain active facets, the uniform ray is the unique regular similarity
family, and every nonzero zero-mean residual produces a non-homothetic
support variation.

The decomposition is compatible with the rotational symmetry group of the
regular dodecahedron. Within the connected support chamber preserving
dodecahedral incidence, each nonregular state is described uniquely by mean
support, shape magnitude, and normalized shape direction. After removal of
absolute scale, the normalized directions lie on a four-sphere in the
five-dimensional zero-mean subspace.

The construction uses only Euclidean geometry, convex polytope theory,
finite-dimensional real linear algebra, and elementary symmetry actions.
It does not classify arbitrary dodecahedra and asserts no mechanical,
dynamical, or physical interpretation.
\end{abstract}

\tableofcontents

\input{sections/01-introduction}
\input{sections/02-euclidean-setting}
\input{sections/03-canonical-split}
\input{sections/04-euclidean-scale-shape}
\input{sections/05-consequences}
\input{sections/06-examples}
\input{sections/07-discussion}
\input{sections/08-conclusion}

\end{document}
